\documentclass{article}
							
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{xcolor}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage[margin=0.7in]{geometry}
	\textheight=700px                    % Saving trees ;-)
\usepackage{url}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

%%% Custom sectioning (sectsty package)
%%% ------------------------------------------------------------
\usepackage{sectsty}

\sectionfont{%			            % Change font of \section command
	\usefont{OT1}{phv}{b}{n}%		% bch-b-n: CharterBT-Bold font
	\sectionrule{0pt}{0pt}{-5pt}{3pt}}


\newcommand{\MyName}[1]{ % Name
		\noindent \Huge \usefont{OT1}{cmr}{b}{n} #1 \hfill 
		\par \normalsize \normalfont}

\newcommand{\MyLocation}[1]{ % Name
		\noindent \usefont{OT1}{cmr}{b}{n} #1 \hfill 
		\par \normalsize \normalfont}

\newcommand{\MyContact}[1]{ % Slogan (optional)
		\large \usefont{OT1}{cmr}{m}{n} #1
		\par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\section*{{\color{gray}\uppercase{#1}}}}

\newcommand{\SkillsEntry}[2]{\textbf{#1}: #2}  
		
\newcommand{\ExperienceEntry}[4]{
		\noindent \textbf{#1} \hfill  
		\hfill #2 \par  % Duration
		\noindent \textit{#3} \par        % School
		\noindent\hangindent=2em\hangafter=0 \small #4 % Description
		\normalsize \par}

\begin{document}

\begin{multicols}{2}
\MyName{Kirill Semin}
\MyLocation{Moscow, Russia}
\columnbreak
\MyContact{\faEnvelope : \href{mailto://qseminq@gmail.com}{qseminq@gmail.com}}
\MyContact{\faGithub : \href{https://www.github.com/DrMatters}{github.com/DrMatters}}
\MyContact{\faLinkedin : \href{https://www.linkedin.com/in/drmatters}{linkedin.com/in/drmatters}}
\end{multicols}

\NewPart{Qualifications}{}


\begin{itemize}
  \item[]{\SkillsEntry{Programming}{Python, Java, C/C++}}
  \item[]{\SkillsEntry{Data Science Frameworks}{Scikit-learn, Pytorch, Pandas, Matplotlib, Seaborn}}
  \item[]{\SkillsEntry{Tools}{Git, Google Cloud Platform, Virtualenv}}
\end{itemize}


\NewPart{Work experience}{}
\ExperienceEntry
{Software Developer Intern}
{Jun 2019 - Sep 2019}
{Yandex N.V. $\vert$ Moscow, Russia}
{	
\begin{itemize}
	\item{Developed an \textbf{intersection finding algorithm} for A/B testing to find and fix statistically dependent experiments.}
	\item{Refactored \textbf{key data source} for recommender system to improve the ability to modify it in A/B tests.}
	\item{Developed functional testing system for one of the services of the product.}
\end{itemize}
}

\NewPart{Independent Projects}{}
\ExperienceEntry
{DeepModerator}
{Nov 2018 - present}
{}
{\begin{itemize}
	\item{Designed and developed the application to simplify forum/social network toxic comments moderation in collaboration with the teammate.}
	\item{Taught myself Python and Machine learning to develop this application and deploy it on Google Cloud Platform.}
	\item{Tested multiple ML models for toxic comments detection using ROC-AUC as metric.}
	\item{Applied \textbf{transfer learning} (context independent embeddings, BERT), \textbf{active machine learning} (human-in-the-loop) and automatic data collection \& interpretation to increase quality of toxicity considering the lack of labeled data.}
\end{itemize}
}
\ExperienceEntry
{HyperoptSearchCV --- {\href{https://github.com/DrMatters/hyperoptsearchcv} {github.com/DrMatters/hyperoptsearchcv}}}
{Jan 2019}
{}
{
While preparing for the competition \textbf{developed} a Python utility which allows using Hyperopt with scikit-learn pipelines. It provides interface similar to GridSearchCV of scikit-learn.
}

\NewPart{Courses}{}
\ExperienceEntry
{Deep Learning Specialization}
{2018}
{Coursera $\vert$ Deeplearning.ai}
{\href{https://www.coursera.org/account/accomplishments/specialization/V5P6NWX4CR95} {Certificate} - Average grade achieved: 99\%.}
\ExperienceEntry
{Machine Learning}
{2018}
{Coursera $\vert$ Stanford \& Andrew Ng}
{\href{https://www.coursera.org/account/accomplishments/certificate/W2FV6BT5XCPF} {Certificate} - Grade achieved: 98.8\%.}

\NewPart{Education}{}
\ExperienceEntry
{Master's degree, Information Systems and Technology}
{2019 - 2021}
{\href{http://bmstu.ru/en}{Bauman Moscow State Technical University} $\vert$ Moscow, Russian Federation}
{}
\ExperienceEntry
{Bachelor's degree, Information Systems and Technology}
{2015 - 2019}
{\href{http://bmstu.ru/en}{Bauman Moscow State Technical University} $\vert$ Moscow, Russian Federation}
{}


\end{document}


